Chapter 3

### 2023-01-17 docs/chapter_03.qmd
add data lineage diagram

---
title: "Chapter 3"
format: html
---

>>>>

---
title: "Chapter 3"
format: html
---
## Trustworthiness of data

```{mermaid}
graph TD
    A[Conflict event] -->|reporter| B(Online news article)
    B --> C

    subgraph GDELT
        C --> |Google Chrome Compact Language Detector - CLD2|D(Language detection)
        D --> |Conditional random field and various lang-specific|E(Word segmentation)
        E --> F(Morphological analysis)
        F --> G(Sentiment and emotional assessment)
        G --> H(Sentence and clause segmentation)
        H --> I(Low pass translation)
        H --> J(Mid pass translation)
        H --> K(Toponymic translation)
        H --> L(Well known entity translation)
        I --> M(Candidate translation ranking)
        M --> O(Chosen translation)
        J --> M
        M --> |some langs|N(High pass translation)
        N --> O
        O --> |Moses and other grammer models|Q(User adaptation - dynamic language models)
        Q --> R(High pass UNK substitution)
        R --> S(Recapitalization models)
        S --> T(English translation, events, entities, geocoding, and scores)

        T --> |Universal Sentence Encoder| U(English article embeddings)

        K --> T
        L --> T

    end

    B --> |human and machine processes|CC(Judgement against ACLED event inclusion criteria)
    subgraph ACLED
        CC --> |human and machine processes|DD[Coded events, categories, event actors, geolocations, reported fatalities]

        DD --> |three rounds of human review|DD
        DD --> EE(Weekly aggregations of events and fatalities)
    end

    EE --> V(Timeseries dataset)
    U --> V

    V --> |Our model| W(Our conflict predictions)

```

## Capstone project timeline
